Towards Spherical Robots for Mobile Mapping in Human Made Environments\tnoteref{mytitlenote}

### 2021-07-13 Latex/sections/stateOfTheArt.tex

The de-facto standard for many SLAM algorithms is the Iterative-Closest-Point (ICP) algorithm~\cite{Besl1992} that employs point-to-point correspondences using closest points, as the name suggests. 
To overcome the requirements on point-density imposed by the point-to-point correspondences instead other correspondences are used. 
In human-made environments, planes are abundantly available and hence provide an attractive base for correspondences.

@@

LOAM~\cite{Zhang2014} is the baseline-algorthm that provides a real-time and lowdrift solution based on two parallel registration algorithms using planes and lines.
Unfortunately, it is not open-source anymore.
LOAM livox extends the LOAM framework to the the rotating prism scanner with small FoV~\cite{Lin_2020}.
Zhou, Wang, and Kaess write that it also adopts the parallel computing to achieve real-time global registration.
Parallel computing needs a powerful CPU, it may be not suitable for an embedded system which has limited computational resources~\cite{Zhou_2021}.
Thus, they extens their smoothing and mapping to the LiDAR and planes case.
In their experiments they used a VLP-16 LiDAR to collect indoor datasets.

>>>>

The de-facto standard for many SLAM algorithms is the Iterative-Closest-Point (ICP) algorithm~\cite{Besl1992} that employs point-to-point correspondences using closest points, as the name suggests. 
To overcome the requirements on point-density imposed by the point-to-point corres\-pon\-den\-ces instead other correspondences are used. 
In human-made environments, planes are abundantly available and hence provide an attractive base for correspondences.

@@

LOAM~\cite{Zhang2014} is the baseline-algorithm that provides a real-time and lowdrift solution based on two parallel registration algorithms using planes and lines.
Unfortunately, it is not open-source anymore.
LOAM livox extends the LOAM framework to the the rotating prism scanner with small FoV~\cite{Lin_2020}.
Zhou, Wang, and Kaess write that it also adopts the parallel computing to achieve real-time global registration.
Parallel computing needs a powerful CPU, it may be not suitable for an embedded system which has limited computational resources~\cite{Zhou_2021}.
Thus, they extend their smoothing and mapping to the LiDAR and planes case.
In their experiments they used a VLP-16 LiDAR to collect indoor datasets.
